\documentclass{article}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{comment}
\usepackage{multicol}
\usepackage[top=0.55in,bottom=.5in,left=.25in,right=.25in,paperheight=11in,paperwidth=8.5in,includefoot]{geometry}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{changepage}

\newcommand\mybar{\kern1pt\rule[-\dp\strutbox]{.8pt}{\baselineskip}\kern1pt}

\addtolength{\topmargin}{-.25in}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule]

\titlespacing*{\section}
{0pt}{2.0ex }{.5ex}

\titleformat{\subsection}
{\large\bfseries}
{--}
{0em}
{}

\titlespacing*{\subsection}
{0pt}{2.0ex }{.1ex}

\titleformat{\subsubsection}[runin]
{\large\bfseries}
{}
{0em}
{}[ --]

\titlespacing*{\subsubsection}
{10pt}{.2ex}{.2ex}

%Try to move page number
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\begin{adjustwidth}{540pt}{10pt}\thepage \end{adjustwidth}}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\begin{center}
	\begin{Huge}
		Zachary W. Walden\\
	\end{Huge}
	\begin{large}
		\textsl{222 Prairie Ridge Dr. Bartlesville, Oklahoma 74006}\\
	\end{large}
	\begin{normalsize}
		\faMobile { (832)-294-9706} \mybar { } \faGithub \href{https://github.com/ZachWWalden}{ ZachWWalden}
		\mybar { }\faEnvelope\href{mailto::zachary.walden@eagles.oc.edu}{ zachary.walden@eagles.oc.edu}
	\end{normalsize}
\end{center}

\begin{adjustwidth}{70pt}{70pt}
\begin{spacing}{1.25}
\vspace*{1.5cm}
%Issues does not get across board design experiecne. Poorly expresses my interpersonal skills.
%Generally not convincing.

\today
\vspace*{.6cm}
\\To whom it may concern,\\

As a recent graduate in Computer Engineering, I am seeking a challenging position applying my knowledge
and  skills designing, building and testing circuit boards. The Design Engineer I position description
matches well with my capabilities.

Per my attached resume, I earned a 4.0/4.0 GPA and graduated summa cum laude. I know the value of hard
work, determination, and completing projects on schedule.

Following my freshman year, I began working as a Java programmer at my Professor's startup VisuaALS Technology Solutions LLC. There I worked on a REST web API using the Spring Framework. The API was used to validate system purchases, by  storing the device unique IMEI number. I designed a SQL database to store hashed instances of those IMEIs. A remote management feature was also added to simplify the addition of new devices into the database.

During university, I was selected as a teaching assistant for a lower division course my sophomore and senior year, and the sole teaching assistant for a series of two upper division courses my senior year.
In those roles, I aided students in debugging hardware and software issues they faced while working with microcontrollers alongside Digital and Analog peripherals.

I was chosen by a professor to experiment with an RGB laser assembly over winter break. I reverse engineered the included 7 color driver board. Using that knowledge, I found a suitable op-amp based current source for driving a grounded load, then built and tested that design using on hand components. Through testing, I found that the university's components were not fast enough. I then developed a list of speed and power requirements, using them to source suitable components. Finally, I assembled and tested 2 PCB revisions designed in KiCad. The second revision added an adjustable current set point with a dual gang potentiometer and incorporated the advanced knowledge in PCB design I acquired during the time between revisions.

Please consider me for this position.
I am available by phone or email, which are listed below and on my resume.\\ \\
Sincerley,
%Signature picture

Zachary Walden

\vspace*{\fill}
\end{spacing}
\end{adjustwidth}

\newpage


\begin{center}
	\begin{Huge}
		Zachary W. Walden\\
	\end{Huge}
	\begin{large}
		\textsl{222 Prairie Ridge Dr. Bartlesville, Oklahoma 74006}\\
	\end{large}
	\begin{normalsize}
		\faMobile { (832)-294-9706} \mybar { } \faGithub \href{https://github.com/ZachWWalden}{ ZachWWalden}
		\mybar { }\faEnvelope\href{mailto::zachary.walden@eagles.oc.edu}{ zachary.walden@eagles.oc.edu}
	\end{normalsize}
\end{center}
\begin{spacing}{.5}

\begin{adjustwidth}{30pt}{30pt}
	\textit{\large{---Seeking a challenging position designing, building, and testing mixed signal systems in a team environment. A position with growth and leadership potential that utilizes my skills, knowledge and experience to provide excellence in product development and manufacturing.
	I will quickly contribute to the success of projects that will improve and expand the product lines for Garmin.}}
\end{adjustwidth}

\section{Skills}
	\subsection{Software}
		\subsubsection{Languages} \large{ C / C++} \small{(Embedded(RTOS, PIC, STM32, AVR), Linux, Windows),}\large{ Python, Assembly} \small{(AVR),} \large{ Verilog} \small{(CocoTb),} \hspace*{1cm}\large{ MATLAB / Simulink, Java} \small{(General, Android),} \large{ Bash}
		\subsubsection{Other} \large{ Docker, GDB, Git, Qt GUI} \small{(Python \& C++),} \large{ General Linux, UML, SYSML, \LaTeX, Agile}
	\subsection{Hardware}
		\subsubsection{Design} \large{ Kicad(Schematic Capture, PCB layout), Cadence Design Entry CIS, Digital} \small{(Microcontrollers, FPGA, 7400 \hspace*{1cm} series)}\large{, Analog} \small{(Op-Amps, Transisitors, Diodes)}
		\subsubsection{Verification / Validation} \large{ Cadence PSpice, Oscilloscopes, Function Generators, Multimeters,\\ \hspace*{1cm} Logic Analyzers, Network Analyzers.}
		\subsubsection{Prototyping} \large{ Breadboard, Iron \& Hot Air, SMT} \small{(Experience with all package types besides BGA, QFN, \& Wafer Scale),} \large{ \hspace*{1cm} THT}

\section{Education}
	\subsection{Oklahoma Christian University}
		\textit{Bachelor of Science, Computer Engineering}, GPA 4.0/4.0, Summa Cum Laude \hfill \small{\textsl{Aug. 2018 - Apr. 2022}}

\section{Honors \& Awards}
	\subsection{Oklahoma Christian University}
		\begin{itemize}[label=$\bullet$,itemsep=-.35ex]
			\item \large{Outstanding ECE Senior} \hfill \small{\textsl{2022}}
			\item \large{Outstanding ECE Junior} \hfill \small{\textsl{2021}}
			\item \large{Outstanding ECE Sophomore} \hfill \small{\textsl{2020}}
			\item \large{The President's Scholarship} \hfill \small{\textsl{2018 - 2022}}
		\end{itemize}
\section{Experience}
	\subsection{Oklahoma Christian University}
		\subsubsection{\large{Professor's Assistant}} \hfill \small{\textsl{Dec. 2020 - Jul. 2021}}
			\begin{itemize}[label=--,itemsep=-.35ex]
				\item \large{Designed 2 revisions of a 3 channel adjustable full color laser diode driver board, using Kicad, to replace a 7 color driver board using an enhanced differential Howland Current Pump}
				\item \large{Selected components to meet the frequency needs in excess of 12 MHz}
				\item \large{Designed and layed out buck converter}
				\item \large{Reverse engineered 7-Color TTL driver board}
			\end{itemize}
		\subsubsection{\large{Teaching Assistant: CENG-3203, CENG-3213, ENGR-1122}} \hfill \small{\textsl{Jan. 2020 - Mar. 2020, Aug. 2021 - Apr. 2022}}
			\begin{itemize}[label=--,itemsep=-.35ex]
				\item \large{Helped students troubleshoot hardware and software issues with 8-bit AVR Microcontrollers \& 74 series logic used to control HD44780 LCD's, Keypad enocoders, and parallel DACs in order to control a laser scanner system}
				\item \large{Instructed students on Assembly language concepts}
				\item \large{Guided students in constructing an autonomous robot}
				\item \large{Debugged Analog \& Digital circuitry, and embedded C written for Microchip's 16-bit dsPIC line}
			\end{itemize}
	\subsection{VisuALS Technology Solutions LLC}
		\subsubsection{\large{Java Programmer}} \hfill \small{\textsl{May. 2019 - Aug. 2020}}
			\begin{itemize}[label=--,itemsep=-.35ex]
				\item \large{Designed a Spring REST API to authenticate a software purchase using a tablet's imei number}
				\item \large{Connected the authentication API to a SQL database that stored the hash of the imei}
				\item \large{Designed a SQL database running on Google's Cloud}
				\item \large{Wrote dynamic Android U.I.}
				\item \large{Researched Machine Learning for text prediction} \small{(Tensorflow, Tensorflow Lite)}
			\end{itemize}

\newpage

\begin{center}
	\begin{huge}
		Zachary W. Walden\\
	\end{huge}
\end{center}

\section{Projects}
	\subsection{8-bit 5-stage Pipeline RISC CPU \hfill \normalfont{\small{\textsl{Jan. 2022 - Apr. 2022}}}}
		\begin{itemize}[label=--,itemsep=-.35ex]
			\item \large{Designed and implemented 32-bit fixed length RISC instruction set comprising 42 instructions.}
			\item \large{Architected and implemented, from scratch, an 8-bit mostly bypassed CPU with a 5 stage integer pipeline in Verilog and run on a Xilinx Spartan 7 board}
			\item \large{Implemented, and integrated a vga sync generator and a dumb framebuffer into the cpu using special instructions to write to the framebuffer}
			\item \large{Wrote a simple assembler for the instruction set in Python along with helper scripts to convert the assembler output into Xilinx's coe format}
			\item \large{Debugged modules using test-benches written using the Cocotb framework for Python, and viewing waveform dumps in GTKWave}
			\item \large{Used Xilinx's Integrated Logic Analyzer IP in conjunction with an internal reset trigger circuit to troubleshoot on chip behavior}
		\end{itemize}
	\subsection{DC/DC Boost Converter \hfill \normalfont{\small{\textsl{Sep. 2020 - Nov. 2020}}}}
		\begin{itemize}[label=--,itemsep=-.35ex]
			\item \large{Designed a discrete boost converter taking a 6V input and giving an adjustable 12V-24V output in steps of .1V using a PIC microcontroller for control}
			\item \large{The design achieved an average of .54\% error relative to the target output voltage}
			\item \large{Used PIC Datasheet and Family Reference Manual to write register level PWM and SPI drivers}
			\item \large{Wrote simple proportional-only control system to stabalize the output voltage, along with a bias adjustment to ensure the correct setpoint was reached}
			\item \large{Designed and assembled a printed circuit board for the project}
			\item \large{Led a 3 person team, delegating responibilities to the comprising members}
		\end{itemize}
\begin{comment}
	\subsection{RGB Laser Scanner Controller}
		\begin{itemize}[label=--,itemsep=-.35ex]
			\item \large{}
		\end{itemize}
\end{comment}

\section{References}
	\subsection{Dr. Jeff Bigelow}
		\begin{itemize}[label=--,itemsep=-.35ex]
			\item \large{Chair, Department of Electrical \& Computer Engineering, Oklahoma Christian University}
			\item \large{\href{mailto::jeff.bigelow@oc.edu}{\large{Email: jeff.bigelow@oc.edu}}}
			\item \large{Office Phone: (405)-425-5448}
			\item \large{Professor, and supervisor for my teaching assistant positons.}
		\end{itemize}
	\subsection{Steven P. Maher, MS.}
		\begin{itemize}[label=--,itemsep=-.35ex]
			\item \large{Associate Professor of Electrical \& Computer Engineering, Oklahoma Christian University}
			\item \large{CEO, VisuALS Technology Solutions LLC.}
			\item \large{\href{mailto::steve.maher@oc.edu}{\large{Email: steve.maher@oc.edu}}}
			\item \large{Office Phone: (405)-425-5407}
			\item \large{Professor, and employer at VisuALS Technology Solutions LLC.}
		\end{itemize}

\end{spacing}
\end{document}
